$p$-adic precision

### 2014-02-07 padicprec.tex
Added a short paragraph about comparison with floating point arithmetics.

@@

This phenomenon is general: if $P$ is a polynomial over $\Q_p$ known at 
some finite precision $O(p^N)$, a root $\alpha$ of $P$ having possibly 
multiplicity $m$ (\emph{i.e.} $P(\alpha), P'(\alpha), \ldots, P^{(m-1)} 
(\alpha)$ vanish at the given precision) can be computed at precision 
roughly $O(p^{N/m})$. However, if we know in advance that $\alpha$ has 
indeed multiplicity $m$ then we can compute it at precision $O(p^{N-c})$ 
where $c$ is some constant.

>>>>

\subsubsection*{Quick comparison with floating point arithmetics}

It worths remarking that the two strategy designed above share many 
similarities with usual floating point arithmetics over the reals. 
Indeed, roughly speaking, in each setting, we begin by choosing a large 
precision, we do all our computations up to this precision understood 
that when we are not sure about some digit, we choose it ``at random'' 
or using good heuristics. The main difference is that, in the 
ultrametric setting, we are able (under some mild hypothesis) to 
quantify the precision we need at each individual step in order to be 
sure that the final result is correct up to the required precision.

@@

This phenomenon is general: if $P$ is a polynomial over $\Q_p$ known at 
some finite precision $O(p^N)$, a root $\alpha$ of $P$ having possibly 
multiplicity $m$ (\emph{i.e.} $P(\alpha), P'(\alpha), \ldots, P^{(m-1)} 
(\alpha)$ vanish at the given precision) can be computed at precision 
roughly $O(p^{N/m})$. However, if we know in advance that $\alpha$ has 
indeed multiplicity $m$ then we can compute it at precision $O(p^{N-c})$ 
where $c$ is some constant (depending on $P$ and $\alpha$ but not on
$N$).
